---
title: | 
 | MT5763: Software for Data Analysis
 | Group Project Shiny App Description
author: "Spencer Percival"
date: "16/11/2020"
output: bookdown::html_document2
nocite: '@*'
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8, out.width = "60%", fig.align = "center")
# Centre plot titles
theme_update(plot.title = element_text(hjust = 0.5))
```

```{r, message = FALSE, results = "hide", warning = FALSE}

# Load necessary libraries
library(tidyverse)
library(devtools)

```

The **private** GitHub repository for the Group Project which this app forms a part of can be accessed using this link: <https://github.com/csheehan10/MT5763_ProperJob.git>

The Shiny app referred to in this report, along with it's documentation, can be found in this **private** GitHub repository: <https://github.com/percivalspencer/MT5763_Shiny.git>

The published Shiny app is publicly accessible through this link: <>

# Abstract

# Introduction

# (APPENDIX) Appendix {-} 

# Session Information for Reproducibility

```{r}

devtools::session_info()

```

